### 2019-10-06 Sections/essay_to_the_future_QKD.tex
adding quantum digital signature intro

\dropcap{Q}{uantum} key distribution (QKD) is the first quantum information task to reach commercialisation. Its purpose is to distribute a secret-key between two trusted parties who share a quantum channel, as well as a classical channel for authentication. Unlike current cryptography systems, which are secure based on the presumed limitations of an adversary's computer (\textit{computational security}\index{Computational!Security}), the security of QKD is based on the laws of quantum mechanics, providing guaranteed security unless our understanding of quantum physics is inherently wrong (\textit{information theoretic security}\index{Information-theoretic!Security}).

@@

>>>>

\dropcap{Q}{uantum} cryptography is the first field in quantum information task to reach commercialisation. At its early stages, quantum cryptography was almost synonymous with quantum key distribution (QKD), but has since branched and became one of the fastest growing areas in quantum information.
The purpose of QKD is to distribute a secret-key between two trusted parties who share a quantum channel, as well as a classical channel for authentication. Unlike current cryptography systems, which are secure based on the presumed limitations of an adversary's computer (\textit{computational security}\index{Computational!Security}), the security of QKD is based on the laws of quantum mechanics, providing guaranteed security unless our understanding of quantum physics is inherently wrong (\textit{information theoretic security}\index{Information-theoretic!Security}). In this section we discuss some of the challenges in QKD, as well as other aspects of quantum cryptography beyond traditional QKD.

@@

% \subsection{Quantum random number generation}

\subsection{Quantum digital signatures}

Classical digital signature is a cryptographic primitive whose purpose is to ensure that a message's 
\begin{enumerate}
\item Authenticity: it was created by the claimed sender
\item Integrity: the message has not been altered
\item Non-repudiation: the sender cannot deny having sent this message
\end{enumerate}

A quantum digital signature (QDS) scheme involves multiple parties, one sender, and potentially many receivers. It consists of three stages, each consists of a corresponding algorithm.

\begin{itemize}
\item Key generation: A private key ($sk$) is given to the sender, and (potentially multiple) public keys ($pk$) are given to the receivers.
\item Signing algorithm: the sender chooses a message $M$ and uses the private key $sk$ to generate a signature, $\sigma = \sigma(M)$. She sends the pair ($M,\sigma(M)$) to the desired receiver(s)
\item Verification: a receiver possesses the message and signature pair ($M,\sigma(M)$) and the public key $pk$, he/she checks whether to accept the message as having originated to the claimed sender.
\end{itemize}

However, to ensure that the parties receive the same and correct public becomes a non-trivial task, if the keys ar equantum. Instead, when dealing with QDS schemes, one often aims to ensure
that the QDS scheme has the following properties:
\begin{enumerate}
\item Unforgeability: a third party cannot send a message pretending to be someone else
\item Trasferability: if a receiver receives a signature, they should be confident that any other receiver should also accept the signature.
\item Non-repudiation: the sender cannot deny having sent this message
\end{enumerate}

There are various protocols that falls under the catagory of QDS, here we deal with the notion
of signing a classical message using quantum communication and quantum computation.

\subsection{Quantum data locking - the quantum enigma machine}
